---
title: "Tomato Color Tester"
author: "Rovin Sharma"
date: "10/26/2020"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---
**This is a ggplot test to use RGB values from the analyzer images to color the points of each species with its corresponding color**
```{r, include = FALSE, message = FALSE, error = FALSE}
library(tidyverse)
```

```{r, include = FALSE, message = FALSE, error = FALSE}
tmtFiles <- read_csv("D:/School/Caicedo Lab/Test.csv")
```
First the columns needed to be renamed since they've got spaces. 
```{r, message = FALSE, error= FALSE}
tmtFiles <- tmtFiles %>%
  rename(image_files = "image files", tomato_pericarp_area = "Tomato Pericarp Area", R = "Average Red", G = "Average Green", B = "Average Blue", tomato_pericarp_area_ratio = "Tomato Pericarp Area Ratio", tomato_pericarp_thickness = "Tomato Pericarp Thickness", tomato_pericarp_thickness_ratio = "Tomato Pericarp Thickness Ratio", avg_luminosity = "Average Luminosity", L = "Average L Value", a = "Average a Value", b = "Average b Value", avg_hue = "Average Hue", avg_chroma = "Average Chroma")
```

Selecting for specific columns. It is not necessary to select R, G, B since the values are pulled from the original files.
```{r, message= FALSE, error= FALSE}
tmtfilesthickness <- tmtFiles %>% 
  select(`image_files`, `tomato_pericarp_thickness`)
```

The ggplot initial aes can not contain the colors from the RGB, for some reason it ends up picking a spectrum rather than the RGB values of specific image files. The best way to go about coloring the points is to actually color in the geom_point arguments, as I've done below.

I've made the points quite large to see the colors, the average values aren't too far apart, I only used a fraction of the images data.
```{r, fig.height= 10, fig.width= 15}
ggplot(data = tmtfilesthickness, aes(x = tomato_pericarp_thickness, y = image_files)) +
  geom_point(size = 6, color = rgb(tmtFiles$R, tmtFiles$G, tmtFiles$B, maxColorValue = 255)) +
  theme_bw()
```

  