---
title: "0805"
author: "Rovin Sharma"
date: "11/3/2020"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---
# This is my first try at creating a cohesive plot using the data collected through Tomato Analyzer.

*I apply here what I've learned through the color test.*

```{r, include = FALSE, message = FALSE, error = FALSE}
library(tidyverse)
library(DT)
```

```{r, message = FALSE, error = FALSE, warning= FALSE}
tmt0805 <- read_csv("D:/School/Caicedo Lab/0805.csv")
```

Each image file contains the first 3 letters as the species name, rather than create a concatenated set of preset names, I just took the first 3 letter from each image_file string name and created a new species column as shown below. The only problem here is that two letter species names, such as SL, will have a - followed by SL.

```{r, message = FALSE, error = FALSE, warning = FALSE}
tmt0805$species <- substr(tmt0805$tomatoes, 1, 3)
tmt0805dt <- tmt0805 %>% 
  select(species, tomatoes, Tomato_Pericarp_Thickness)
datatable(head(tmt0805dt, 100))
```

```{r}
tmt0805thickness <- tmt0805 %>%
  filter(!is.na(R))
```

This is my first plot after trying to figure out how to group species. Using the substring method seems to have worked, and the results look good, except for the one lonely sc with 1 sample size ):

```{r, warning = FALSE}
ggplot(data = tmt0805thickness, aes(x = Tomato_Pericarp_Thickness, y = species))+
  geom_boxplot() +
  geom_jitter(color = rgb(tmt0805thickness$R, tmt0805thickness$G, tmt0805thickness$B, maxColorValue = 255), alpha = 0.7) +
  theme_bw()
```

Here I am just messing with another variable, area, just to make sure everything works. 

```{r}
ggplot(data = tmt0805thickness, aes(x = Area, y = species))+
  geom_violin() +
  geom_jitter(color = rgb(tmt0805thickness$R, tmt0805thickness$G, tmt0805thickness$B, maxColorValue = 255), alpha = 0.7) +
  theme_bw()
```

**The benefit of using avg RGB values as a comparative variable.**

Here the points are color coded based on each individual tomato's corresponding RGB values. This allows for us to see whether there is or is not correlation between color and multiple variables at the same time. Unlike the plot below this one, there is no metric for the color values, it's simply used for preliminary analysis, but it can be valuable for distinguishing between species without putting in too much computational work. I'm sure Jake can make some good use of this.

```{r}
ggplot(data = tmt0805thickness, aes(x = Area, y = Tomato_Pericarp_Thickness))+
  geom_point(size = 2, color = rgb(tmt0805thickness$R,tmt0805thickness$G, tmt0805thickness$B, maxColorValue = 255)) +
  #geom_jitter(color = rgb(tmt0805thickness$R, tmt0805thickness$G, tmt0805thickness$B, maxColorValue = 255), alpha = 0.7) +
  theme_bw()
```

**Using individual RGB values to understand other color values better**

Chroma is a measurement of how much color is stripped away by adding grays, whites, or blacks. Higher chroma indicates more saturation or brightness. Naturally, green tomatoes exhibit lower chroma because reds in tomatoes are much more vibrant than greens.

This is another example of how the RGB values for each individual is valuable as a passive comparative variable. While the chroma gives us some numerical data, it means little if the color of the tomato isn't seen (Especially to someone who doesn't understand color values). This is a good way of comparing color values while also having a better understanding of what we are looking at. In this particular case, knowing that the tomatoes on the lower end of the X axis are green helps comprehend the meaning of the chroma value.

```{r}
ggplot(data = tmt0805thickness, aes(x = Average_Chroma, y = species))+
  geom_boxplot() +
  geom_jitter(color = rgb(tmt0805thickness$R, tmt0805thickness$G, tmt0805thickness$B, maxColorValue = 255), alpha = 0.9) +
  theme_bw()
```